Anony\emph{mice}d shareable data: Using \emph{mice} to create and analyze multiply imputed synthetic data sets

### 2021-11-01 manuscript/Manuscript.Rmd
Update manuscript

The sampling distribution of the means of the continuous variables for both the bootstrapped and the synthetic data can be found in Figure 1, while the number of observations per category in the bootstrapped data and the averaged number of observations per category over the synthetic data sets can be found in Figure 2.

```{r univariate-statistics, echo = FALSE, cache = TRUE, results = FALSE}
library(xtable)
true <- psych::describe(data)

@@

bind_rows(Boostrapped = boot_stats_cont, 
          Synthetic = syn_stats_cont, 
          .id = "Class") %>%
  ggplot(aes(x = mean, col = Class, fill = Class)) +
  geom_density(alpha = 0.5) +
  facet_wrap(~name, scales = "free") +
  theme_minimal() +
  scale_fill_brewer(palette = "Set1") +
  scale_color_brewer(palette = "Set1") +
  labs(x = "Mean",
       title = "Empirical sampling distribution of the mean.")
```

Both figures show that the marginal distributions of the bootstrapped data and the synthetic data are highly similar. Additionally, the univariate descriptives for the original data and the synthetic data can be found in Table 2.

```{r univariate-statistics-II, echo = FALSE, cache = TRUE, results = FALSE}
boot_stats_cat <- bootstrap_samples %>%
  map_dfr(~.x %>%
            select(!where(is.numeric)) %>%
            mutate(across(everything(), as.character)) %>%
            pivot_longer(everything()) %>% 
            group_by(name, value) %>%
            summarize(`Number of observations` = n(), .groups = "drop"))

@@

bind_rows(Boostrapped = boot_stats_cat, 
          Synthetic = syn_stats_cat, 
          .id = "Class") %>%
  ggplot(aes(y = value, x = `Number of observations`, col = Class, group = Class)) +
  geom_point(alpha = 0.1, position = position_jitterdodge(jitter.width = 0.2)) +
  facet_wrap(~name, scales = "free") +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  labs(x = "Number of observations per category",
       title = "Distribution of data over different categories.")

bind_rows(true, setNames(synth, names(true))) %>% 
           arrange(vars) %>% .[, c(2:5, 8:9, 11:12)] %>% round(3) %>% 
  xtable
```
<!-- % latex table generated in R 4.1.0 by xtable 1.8-4 package -->
<!-- % Mon Oct  4 16:47:59 2021 -->
\begin{table}[ht]
\caption{Univariate descriptives for the true data and $m=5$ pooled univariate descriptives for the synthetic data over 1000 simulations. Variable names followed by a $^*$ are categorical.}
\centering
\begin{tabular}{rrrrrrrrr}
  \hline
 & n & mean & sd & median & min & max & skew & kurtosis \\ 
  \hline
original age & 748 & 9.16 & 6.89 & 10.50 & 0.04 & 21.18 & -0.03 & -1.56 \\ 
  synthetic age & 748 & 9.15 & 6.89 & 10.49 & 0.04 & 20.96 & -0.03 & -1.55 \\ 
  original hgt & 748 & 131.10 & 46.52 & 145.75 & 50.00 & 198.00 & -0.30 & -1.47 \\ 
  synthetic hgt & 748 & 131.06 & 46.50 & 145.32 & 50.69 & 197.16 & -0.30 & -1.47 \\ 
  original wgt & 748 & 37.12 & 26.03 & 34.55 & 3.14 & 117.40 & 0.38 & -1.03 \\ 
  synthetic wgt & 748 & 37.09 & 26.00 & 34.44 & 3.35 & 112.26 & 0.38 & -1.03 \\ 
  original bmi & 748 & 18.04 & 3.04 & 17.45 & 11.73 & 31.74 & 1.14 & 1.79 \\ 
  synthetic bmi & 748 & 18.05 & 3.08 & 17.48 & 11.49 & 32.37 & 1.11 & 1.85 \\ 
  original hc & 748 & 51.62 & 5.86 & 53.10 & 33.70 & 65.00 & -0.91 & 0.12 \\ 
  synthetic hc & 748 & 51.61 & 5.86 & 53.18 & 34.38 & 62.85 & -0.91 & 0.12 \\ 
  original gen* & 748 & 2.53 & 1.59 & 2.00 & 1.00 & 5.00 & 0.52 & -1.36 \\ 
  synthetic gen* & 748 & 2.53 & 1.59 & 2.00 & 1.00 & 5.00 & 0.52 & -1.35 \\ 
  original phb* & 748 & 2.75 & 1.86 & 2.00 & 1.00 & 6.00 & 0.56 & -1.25 \\ 
  synthetic phb* & 748 & 2.75 & 1.86 & 2.00 & 1.00 & 6.00 & 0.56 & -1.24 \\ 
  original tv & 748 & 8.43 & 8.12 & 3.00 & 1.00 & 25.00 & 0.85 & -0.78 \\ 
  synthetic tv & 748 & 8.42 & 8.11 & 3.19 & 1.00 & 25.00 & 0.85 & -0.77 \\ 
  original reg* & 748 & 3.02 & 1.14 & 3.00 & 1.00 & 5.00 & -0.08 & -0.77 \\ 
  synthetic reg* & 748 & 3.02 & 1.14 & 3.00 & 1.00 & 5.00 & -0.08 & -0.76 \\ 
   \hline
\end{tabular}
\end{table}

>>>>

The sampling distribution of the means of the continuous variables for both the bootstrapped and the synthetic data can be found in Figure 1, while the number of observations per category in the bootstrapped data and the averaged number of observations per category over the synthetic data sets can be found in Figure 2. Both figures show that the marginal distributions of the bootstrapped data and the synthetic data are highly similar. Additionally, the univariate descriptives for the original data and the synthetic data can be found in Table 2.

```{r univariate-statistics, echo = FALSE, cache = TRUE, results = FALSE, fig.cap="Empirical sampling distribution of the bootstrapped and synthetic means of the continuous variables in the boys data."}

library(xtable)

true <- psych::describe(data)

@@

bind_rows(Boostrapped = boot_stats_cont, 
          Synthetic = syn_stats_cont, 
          .id = "Class") %>%
  ggplot(aes(x = mean, col = Class, fill = Class)) +
  geom_density(alpha = 0.5) +
  facet_wrap(~name, scales = "free") +
  theme_classic() +
  theme(legend.position = "bottom") +
  scale_fill_brewer(palette = "Set1") +
  scale_color_brewer(palette = "Set1") +
  labs(x = "Mean",
       y = "Density",
       title = "")
```

```{r univariate-statistics-II, echo = FALSE, cache = TRUE, results = FALSE, fig.cap = "Empirical sampling distribution of the number within each category of the categorical variables in the bootstrapped and synthetic boys data."}
boot_stats_cat <- bootstrap_samples %>%
  map_dfr(~.x %>%
            select(!where(is.numeric)) %>%
            mutate(across(everything(), as.character)) %>%
            pivot_longer(everything()) %>% 
            group_by(name, value) %>%
            summarize(`Number of observations` = n(), .groups = "drop"))

@@

bind_rows(Boostrapped = boot_stats_cat, 
          Synthetic = syn_stats_cat, 
          .id = "Class") %>%
  ggplot(aes(y = value, x = `Number of observations`, fill = Class)) +
  geom_boxplot(position = "dodge", width = 0.8) +
  facet_wrap(~name, scales = "free") +
  theme_classic() +
  theme(legend.position = "bottom") +
  scale_fill_brewer(palette = "Set1") +
  labs(x = "Number of observations per category",
       y = "Category",
       title = "")
```

```{r, include = FALSE}
bind_rows(true, setNames(synth, names(true))) %>% 
           arrange(vars) %>% .[, c(2:5, 8:9, 11:12)] %>% round(3) %>% 
  xtable
```
<!-- % latex table generated in R 4.1.0 by xtable 1.8-4 package -->
<!-- % Mon Oct  4 16:47:59 2021 -->
\begin{table}[ht]
\caption{Univariate descriptives for the true data and $m=5$ pooled univariate descriptives for the synthetic data over 1000 simulations. Variable names followed by a $^*$ are categorical.}
\centering
\begin{tabular}{rrrrrrrrr}
  \hline
 & n & mean & sd & median & min & max & skew & kurtosis \\ 
  \hline
original age & 748 & 9.16 & 6.89 & 10.50 & 0.04 & 21.18 & -0.03 & -1.56 \\ 
  synthetic age & 748 & 9.15 & 6.89 & 10.49 & 0.04 & 20.96 & -0.03 & -1.55 \\ 
  original hgt & 748 & 131.10 & 46.52 & 145.75 & 50.00 & 198.00 & -0.30 & -1.47 \\ 
  synthetic hgt & 748 & 131.06 & 46.50 & 145.32 & 50.69 & 197.16 & -0.30 & -1.47 \\ 
  original wgt & 748 & 37.12 & 26.03 & 34.55 & 3.14 & 117.40 & 0.38 & -1.03 \\ 
  synthetic wgt & 748 & 37.09 & 26.00 & 34.44 & 3.35 & 112.26 & 0.38 & -1.03 \\ 
  original bmi & 748 & 18.04 & 3.04 & 17.45 & 11.73 & 31.74 & 1.14 & 1.79 \\ 
  synthetic bmi & 748 & 18.05 & 3.08 & 17.48 & 11.49 & 32.37 & 1.11 & 1.85 \\ 
  original hc & 748 & 51.62 & 5.86 & 53.10 & 33.70 & 65.00 & -0.91 & 0.12 \\ 
  synthetic hc & 748 & 51.61 & 5.86 & 53.18 & 34.38 & 62.85 & -0.91 & 0.12 \\ 
  original gen* & 748 & 2.53 & 1.59 & 2.00 & 1.00 & 5.00 & 0.52 & -1.36 \\ 
  synthetic gen* & 748 & 2.53 & 1.59 & 2.00 & 1.00 & 5.00 & 0.52 & -1.35 \\ 
  original phb* & 748 & 2.75 & 1.86 & 2.00 & 1.00 & 6.00 & 0.56 & -1.25 \\ 
  synthetic phb* & 748 & 2.75 & 1.86 & 2.00 & 1.00 & 6.00 & 0.56 & -1.24 \\ 
  original tv & 748 & 8.43 & 8.12 & 3.00 & 1.00 & 25.00 & 0.85 & -0.78 \\ 
  synthetic tv & 748 & 8.42 & 8.11 & 3.19 & 1.00 & 25.00 & 0.85 & -0.77 \\ 
  original reg* & 748 & 3.02 & 1.14 & 3.00 & 1.00 & 5.00 & -0.08 & -0.77 \\ 
  synthetic reg* & 748 & 3.02 & 1.14 & 3.00 & 1.00 & 5.00 & -0.08 & -0.76 \\ 
   \hline
\end{tabular}
\end{table}

### 2021-11-01 manuscript/Manuscript.tex
Update manuscript

The sampling distribution of the means of the continuous variables for
both the bootstrapped and the synthetic data can be found in Figure 1,
while the number of observations per category in the bootstrapped data
and the averaged number of observations per category over the synthetic
data sets can be found in Figure 2.

\includegraphics{Manuscript_files/figure-latex/univariate-statistics-1.pdf}

Both figures show that the marginal distributions of the bootstrapped
data and the synthetic data are highly similar. Additionally, the
univariate descriptives for the original data and the synthetic data can
be found in Table 2.

\includegraphics{Manuscript_files/figure-latex/univariate-statistics-II-1.pdf}

@@

\begin{verbatim}
## Loading required package: lattice
\end{verbatim}

\begin{verbatim}
## 
## Attaching package: 'caret'
\end{verbatim}

\begin{verbatim}
## The following object is masked from 'package:future':
## 
##     cluster
\end{verbatim}

\begin{verbatim}
## The following object is masked from 'package:purrr':
## 
##     lift
\end{verbatim}

>>>>

The sampling distribution of the means of the continuous variables for
both the bootstrapped and the synthetic data can be found in Figure 1,
while the number of observations per category in the bootstrapped data
and the averaged number of observations per category over the synthetic
data sets can be found in Figure 2. Both figures show that the marginal
distributions of the bootstrapped data and the synthetic data are highly
similar. Additionally, the univariate descriptives for the original data
and the synthetic data can be found in Table 2.

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/univariate-statistics-1.pdf}
\caption{Empirical sampling distribution of the bootstrapped and
synthetic means of the continuous variables in the boys data.}
\end{figure}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/univariate-statistics-II-1.pdf}
\caption{Empirical sampling distribution of the number within each
category of the categorical variables in the bootstrapped and synthetic
boys data.}
\end{figure}

@@
